|

### 2021-11-01 paper/dcpo_demsupport.Rmd
preparing for the tables

title: |
  | Democracy, Public Support, 
  | and Measurement Uncertainty
thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: August 20, 2021."

author: "Yuehong 'Cassandra' Tai^[University of Iowa], Yue Hu^[Tsinghua University], and Frederick Solt$^{\\dagger}$"

@@

date: "August 20, 2021"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 12pt
indent: true
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography_text: 
  - dcpo_demsupport_text.bib
bibliography_app: 
  - dcpo_demsupport_app.bib
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
      - \usepackage{titlesec}
      - \titleformat*{\section}{\normalsize\bfseries}
      - \titleformat*{\subsection}{\normalsize\itshape}
---

(Word count: 3986)

@@

# load all the packages you will use below 
p_load(
  # analysis
  plm, 
  # presentation
  gridExtra,
  # drhutools, # for colorful plots
  dotwhisker, 
  latex2exp,
  # data wrangling
  here,
  broom,
  tidyverse, 
  glue
)

@@

# dotwhisker::small_multiple() hacks
body(small_multiple)[[17]] <- substitute(
  p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
                      x = as.factor(model), colour = submodel)) +
    do.call(geom_pointrange, point_args) + 
    ylab("") + xlab("") + 
    facet_grid(term ~ .,
               scales = "free",
               labeller = label_parsed,    # enable LaTeX facet labels
               switch = "y") +             # put facet labels on left
    scale_y_continuous(position = "right") # put axis label on right
)

@@

# Online Supplementary Information {-}
# (APPENDIX) Appendix {-}

>>>>

title: |
  | Democracy, Public Support, 
  | and Measurement Uncertainty
# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."

# author:
# - name: Yuehong 'Cassandra' Tai
#   affiliation: University of Iowa
# - name: Yue Hu
#   affiliation: Tsinghua University
# - name: Frederick Solt
#   affiliation: University of Iowa

@@

date: " "
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 12pt
indent: true
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography_text: 
  - dcpo_demsupport_text.bib
bibliography_app: 
  - dcpo_demsupport_app.bib
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{pdflscape} #\usepackage{lscape} better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
      - \newcommand{\blandscape}{\begin{landscape}}
      - \newcommand{\elandscape}{\end{landscape}}
      - \usepackage{titlesec}
      - \titleformat*{\section}{\normalsize\bfseries}
      - \titleformat*{\subsection}{\normalsize\itshape}
---

(Word count: 3888)

@@

# load all the packages you will use below 
p_load(
  # analysis
  plm, 
  # presentation
  gridExtra,
  modelsummary,
  # drhutools, # for colorful plots
  dotwhisker, 
  latex2exp,
  # data wrangling
  here,
  broom,
  tidyverse, 
  glue
)

@@

# dotwhisker::small_multiple() hacks
body(small_multiple)[[19]] <- substitute(
  p <- ggplot(df, aes(y = estimate, ymin = conf.low, ymax = conf.high, 
                      x = as.factor(model), colour = submodel)) +
    do.call(geom_pointrange, point_args) + 
    ylab("") + xlab("") + 
    facet_grid(term ~ .,
               scales = "free",
               labeller = label_parsed,    # enable LaTeX facet labels
               switch = "y") +             # put facet labels on left
    scale_y_continuous(position = "right") # put axis label on right
)

@@

# Online Supplementary Information Appendix {-}
# (APPENDIX) Appendix {-}
